---
title: 'Assignment #12:'
author: "David Vidal"
date: "2025-11-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R markdown
R markdown is a document that allows text, R code, output from said code and formatting needed. When finished constructing the file, 
it can then be turned into an HTML webpage, PDF, Word document or other formats. The formatting is the following; ** ** to make a text bold, 
* * to make a text italic, #s corresponds to the headings, and to write code is```{r}
When knitting the document, the code is run top down, running by chunks. 

## LaTeX expression
$x^2 + 7x - 3$
$$x^2 + 7x - 3$$

### R Code block 1
```{r}

data("cars")

summary(cars)
```

#### R code block 2
```{r}
library(ggplot2)

data("cars")

ggplot(cars, aes(x = speed, y = dist)) + 
  geom_point()
```

##### Conclusion 
I believe that using markdown is extremely helpful, plus can be presented easier and better than just writing a plain report. R markdown allows the individual to use many things in order to report findings easier. 